---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# athletes

<!-- badges: start -->
<!-- badges: end -->

The goal of `athletes` is to provide the tools and data used for the IND athletes dataset, which contains data from 31 subjects.

## Installation

You can install the development version of athletes like so:

``` r
# install.packages("remotes")
remotes::install_github("matcasti/athletes")
```

## Example

This is a basic example which shows you how to call the dataset:

```{r example}
library(athletes)

head(ind[, 1:8]) # First six observations from the first eight columns
```

Lets check the mean values of key HRV metrics for each time point:

```{r cars}
ind[, lapply(.SD, mean), .SDcols = 5:8, keyby = time]
```

You can also plot the data using the classic base-r system:

```{r ind, echo = FALSE}
plot(ind[, 3:8])
```


